Presentation report

### 2024-10-22 Docs/Presentation.Rmd
remake figure for presentation

```{r sim, fig.height=4, fig.width=10}
bind_rows(sim1 %>% mutate(sim = "Simulation 1"), sim2 %>% mutate(sim = "Simulation 2")) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"), linetype = "dashed")+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), na.rm=T, linewidth = 1.0)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), na.rm=T, linewidth = 1.0)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), na.rm=T, linewidth = 1.0)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), na.rm=T, linewidth = 1.0)+
  facet_grid(rows = vars(sim), cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "right")+
  scale_color_manual(values = cols)
```

@@

```{r load_nhanes_result}
# df_nhanes <- read_rds(here("Data/nhanes_bi.rds"))
load(here("Data/ApplOutput_fGFPCA.RData"))
load(here("Data/ApplOutput_GLMMadaptive.RData"))

@@

```{r fig_appl_paper, fig.height=4, fig.width=10}
# redefine color scale
cols <- cols[1:3] 
names(cols) <- c("6am", "12pm", "6pm")

>>>>

```{r sim, fig.height=4, fig.width=10}
bind_rows(sim1 %>% mutate(sim = "Original Sample"), sim2 %>% mutate(sim = "Reduced sample")) %>%
  ggplot()+
  geom_point(aes(x=t, y=Y), size = 0.2)+
  geom_line(aes(x=t, y=eta_i, col = "True"), linetype = "dashed")+
  geom_line(aes(x=t, y=pred0.2, col = "0.2"), na.rm=T, linewidth = 1.0)+
  geom_line(aes(x=t, y=pred0.4, col = "0.4"), na.rm=T, linewidth = 1.0)+
  geom_line(aes(x=t, y=pred0.6, col = "0.6"), na.rm=T, linewidth = 1.0)+
  geom_line(aes(x=t, y=pred0.8, col = "0.8"), na.rm=T, linewidth = 1.0)+
  facet_grid(rows = vars(sim), cols = vars(method))+
  labs(col = "Maximum observation time", x = "Time", y="")+
  scale_x_continuous(breaks = seq(0, 1, by = 0.2))+
  theme(legend.position = "right")+
  scale_color_manual(values = cols)
```

@@

```{r load_nhanes_result, eval=F}
# df_nhanes <- read_rds(here("Data/nhanes_bi.rds"))
load(here("Data/ApplOutput_fGFPCA.RData"))
load(here("Data/ApplOutput_GLMMadaptive.RData"))

@@

```{r fig_appl_paper, fig.height=4, fig.width=10, eval=F}
# redefine color scale
cols <- cols[1:3] 
names(cols) <- c("6am", "12pm", "6pm")
